Clouds and Radiation in a mock-Walker Circulation

### 2019-11-01 Silvers_WalkerCell.tex

>>>>

The reality is that we 
  were also inspired by Schneider et al. 2017.  Is it possible to tie all that together in a sensible way?  
Johnson et al. discusses the trade inversion and the high statitic stability in the subtropics.  He contrasts 
the thermodynamic arguments of Kloesel and Albrecht (1989) 
  and Sun and Lindzen (1993) with the dynamic-thermodynamic argument of Schubert et al. 1995.  What say I?}
